Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-01-20 eswc-2012/phdsymp.tex
no entailment
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@105 43ef1190-90fd-4dd7-a769-d0121f02b80e

The above relies on data and queries that are representative of the
system as a whole. It is often asserted that it is not possible to
create a ``one-size-fits-all'' benchmark (see
e.g. \cite{Schmidt:2011:FBS:2063016.2063054}) to cover all aspects of
an application. While that may be true in the general case, I want to
challenge the assumption that a best effort approach is all we can do
in the case of SPARQL.

@@

\bibliographystyle{plain-csmin}
%\bibliographystyle{splncs03}
\bibliography{selectivity,federation,benchmarks,optimization}

>>>>

The above relies on data and queries that are representative of the
system as a whole. It is often asserted that it is not possible to
create a ``one-size-fits-all'' benchmark (see
e.g. \cite{Schmidt:2011:FBS:2063016.2063054}) to cover all aspects of
an application. While that may be true in the general case, I want to
challenge the assumption that a best effort approach is all we can do
in the case of SPARQL (excluding entailment).

@@

\bibliographystyle{plain-csmin}
%\bibliographystyle{jbact}
%\bibliographystyle{splncs03}
\bibliography{selectivity,federation,benchmarks,optimization}
